\large Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping

### 2018-06-09 Conference/SIMPAR 2016/SIMPAR2016 (1).tex
added Conference folder

\documentclass[letterpaper, 10pt]{ieeeconf}
\IEEEoverridecommandlockouts \overrideIEEEmargins
\usepackage{amsmath,amssymb,url,times,subfigure,graphicx,theorem}
\usepackage{graphicx,subfigure,hyperref}
\usepackage{color,comment}
\usepackage{csquotes}

%\usepackage{refcheck}

%\usepackage{epic,eepic}

\usepackage[]{algorithm2e}

@@

\title{\LARGE \bf
Autonomous Exploration by Expected Information Gain from Probabilisitic Occupancy Grid Mapping
%Autonomous Exploration by Predictive Information Gain from Probabilisitic Occupancy Grid Mapping
%Autonomous Exploration by Predictive Occupancy Grid Mapping
%Autonomous Exploration by Predicting Occupancy Grid Maps
}

@@

\newcommand{\EditTL}[1]{{\color{red}\protect #1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Occupancy grid maps are spatial representations of environments, where the space of interest is decomposed into a number of cells that are considered either occupied or free. This paper focuses on exploring occupancy grid maps by predicting the uncertainty of the map. Based on recent improvements in computing occupancy probability, this paper presents a novel approach for selecting robot poses designed to maximize expected map information gain represented by the change in entropy. This result is simplified with several approximations to develop an algorithm suitable for real-time implementation. The predicted information gain proposed in this paper, in conjunction with an existing motion planner to avoid obstacles, yield an effective autonomous exploration strategy, which is illustrated by numerical examples. 
\end{abstract}

@@

Robotic mapping is the process of generating maps, which represent the environment in close proximity of a robot. The popular occupancy grid mapping representation provides information about the free and occupied space as the robot measures its surroundings~\cite{ThrBurFox05}. Occupancy grid mapping is commonly used while estimating robot location and orientation, known as simultaneous localization and mapping (SLAM). Several SLAM approaches are applied to a variety of problems when mobile robots traverse through an environment to generate a map, but the trajectories are assumed given (e.g.~\cite{ThrBurFox05,DurBai06,CheChe09}). A major problem is that an effective trajectory would be unavailable knowing little or nothing about an environment. 
Autonomous exploration solves this problem, by choosing robotic motion through uncertain space, while building a map that is used for subsequent navigation~\cite{Yam97}.
In this paper, a robot chooses a trajectory designed to maximize information gain of the occupancy grid map.

@@

In this paper, we propose an autonomous exploration technique based on expected entropy change that avoids the aforementioned issues. 
%The occupancy grid mapping scheme is based on~\cite{KauLeeAiMos16}, which provides the exact solution of occupancy grid mapping of a single measurement ray. 
We develop a solution for expected entropy gain based on exact occupancy grid mapping~\cite{KauLeeAiMos16}. This solution directly calculates expected entropy from a probabilistic map based on similar assumptions of those applied to occupancy grid mapping.
Though more accurate than several other approaches, the proposed solution requires large computational resources, making real-time implementation difficult in certain scenarios.
Thus, we provide the tools to approximate the exact solution that reduce the computational requirements with realistic assumptions.
The motion of the robot is formulated as an optimization problem, where the expected entropy change is minimized, or equivalently the expected information gain is maximized.
In short, this paper presents an accurate and computationally-efficient approach to predict map information gain for autonomous exploration with a novel structure that avoids several common assumptions and approximations.

@@

Consider a reduced map, namely $r_l$, composed of only $n_{r,l}$ grid cells that the $l$-th measurement ray intersects, indexed by increasing distance from the robot. Let the $k$-th cell of $r_l$, namely $\mathbf{r}_{l,k}$, correspond to $\mathbf{m}_i$, i.e., $\mathbf{r}_k=\mathbf{m}_i$ and $\bar{\mathbf{r}}_k=\bar{\mathbf{m}}_i$.
From~\cite{KauLeeAiMos16}, the inverse sensor model of the individual grid cell $\mathbf{m}_i$ is
\begin{align}
\label{eqn:InvSenModWithProbDens}
&P(\mathbf{m}_i|z_{t,l},X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l}
P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1})\nonumber\\
&\quad\times \bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\
&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\nonumber\\
&\quad + \bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,k+},X_t)
\bigg],
\end{align}
where $\mathbf{r}_{l,k+}$ corresponds to all $r_l$ such that cells with index less than $k$ are free, the $k$-th cell is occupied, and cells with greater index are irrelevant. Put differently, the $k$-th cell is the closest occupied cell along the $l$-th ray. The normalizer is defined as
\begin{align}
\label{eqn:allEta}
\eta_{t,l}
&=
\bigg[\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]^{-1}.
\end{align}
This approach to obtain the inverse sensor model is advantageous because of computational efficiency and accuracy, obtaining the exact solution in $\mathcal O(n_{r,l}+1)$ operations for \emph{all} grid cells visible by this measurement ray. In occupancy grid mapping, one may use \refeqn{InvSenModWithProbDens} and \refeqn{allEta} in real-time to avoid common approximations or learned solutions.

@@

We consider $100$ probabilistic maps to obtain Monte Carlo results to evaluate the approximate entropy. In every Monte Carlo trial, each grid cell has an $80\%$ chance of being free, and the remaining $20\%$ of grid cells are given an a priori probability uniformly distributed between $0$ and $1$. 
Several metrics serve to evaluate $\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]$ with $\text{E}[H_\text{approx}(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]$. The median expected entropy change is $\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]-H(P(m|X_{1:t},Z_{1:t}))=-0.83792$. The error for the $100$ Monte Carlo cases is defined simply as
\begin{align}
e_{H}&=\frac1{100}\sum_{i=1}^{100}\text{abs}\bigg(\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]\nonumber\\&\qquad\quad-\text{E}[H_\text{approx}(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]\bigg).
\end{align}
The Monte Carlo trials are repeated for $\hat n=\braces{1,2,\ldots,10}$ and the results are plotted in Figure \ref{fig:ApproxJust}.
This example shows a typical case when the summation limits generated from \refeqn{ProbOfFirstCell} have only small effects on \refeqn{HRayComplete}, while providing very large improvements in reducing computation.

\begin{figure}
\centerline{
	\subfigure[Entropy Error]
		{\includegraphics[height=0.35\columnwidth]{JustifyApprox_eH.pdf}
	}	
	\subfigure[Computation Ratio]
		{\includegraphics[height=0.35\columnwidth]{JustifyApprox_tRatio.pdf}
	}
}
\caption{The entropy error is decreased at the cost of increasing computation time in this Monte Carlo 1D measurement ray expected entropy case.}
\label{fig:ApproxJust}
\end{figure}

@@

The robot pose at a future time step is selected to maximize \refeqn{ObjFun} over the search space $\Re^2\times\Sph^1$. We reduce the search by discretizing the search space in both position and attitude as follows. First, we choose $n_c$ candidate locations evenly-spaced along a circle of radius $\delta$, centered around the current location $x_t$, where the $c$-th candidate location is denoted $x_c\in\braces{x_1,x_2,\ldots,x_{n_c}}$. Any location that violates \refeqn{CollisionInequalityConstraint} is excluded to avoid collisions. For each collision-free candidate location, we consider $n_d$ evenly-spaced directions. The rays and attitudes at $x_c$ are denoted $\braces{z_{c,1},z_{c,2},\ldots,z_{c,n_d}}$ and $\braces{R_{c,1},R_{c,2},\ldots,R_{c,n_d}}$, respectively, where the scan with attitude $R_{c,d}$ might cover several ray directions depending on the sensor field of view (FOV). For each candidate location, we choose optimal attitude $R_c^*$ as the summation of the expected entropy changes covered by the scan,
\begin{align}
\label{eqn:FindRc}
&R_c^*=\argmax_{R_{c,d}}\sum_{z_{c,i}\in R_{c,d}\text{ FOV}}\bigg(H(P(m|X_{1:t},Z_{1:t}))\nonumber\\&\qquad\quad\quad\quad\quad-\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,i}))]\bigg).
%\mathcal I_\text{ray}(x_c,z_{c,i})\right).
\end{align}

@@

\begin{figure}
\centerline{
	\includegraphics[height=0.35\columnwidth]{ExampleOptimalPose.png}
}
\begin{picture}(0,0)(0,0)
\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\put(4.4,2.1){\color{blue}$X_t$}
\put(5.9,1.9){\color{red}$x_1$}
\put(2.9,2.0){\color{red}$x_5$}
\put(4.4,3.6){\color{red}$x_3$}
\put(4.4,0.6){\color{red}$x_7$}
\put(5.4,3.0){\color{red}$x_2$}
\put(3.3,3.1){\color{red}$x_4$}
\put(3.3,1.0){\color{red}$x_6$}
\put(5.4,1.0){\color{red}$x_8$}
\put(6.8,3.1){\color{red}$z_{2,1}$}
\put(4.5,3.1){\color{red}$z_{2,5}$}
\put(5.6,4.1){\color{red}$z_{2,3}$}
\put(5.6,2.2){\color{red}$z_{2,7}$}
\put(6.5,3.7){\color{red}$z_{2,2}$}
\put(4.9,3.8){\color{red}$z_{2,4}$}
\put(5.0,2.5){\color{red}$z_{2,6}$}
\put(6.5,2.5){\color{red}$z_{2,8}$}
\put(6.1,2.9){$X_c^*$}
\end{picture}
\caption{Initially, a robot (blue circle) views down and left (blue sector). Then, the robot considers $n_c=8$ poses (red circles) as possible candidates for where to move next. For each candidate, $n_d=8$ directions are considered (red lines, only displayed on candidate location $c=2$). Then, the expected entropy of each ray is calculated. The scan (red sector) covering those rays with the largest expected entropy decreases is chosen for each candidate, and the best candidate $X_c^*$ (black circle: location, black sector: scan) is chosen to maximize information gain. Finally, a wavefront planner provides the collision-free motion between $X_t$ and $X_c^*$, and the process is repeated.
}
\label{fig:OptProcess}
\end{figure}

@@

The objective function of the optimal pose $X_c^*=\braces{x_c^*,R_c^*}$ must satisfy $\mathcal I(X_c^*)\geq\mathcal I_\text{min}$ to avoid motions where little information is expected to be gained. 
If this condition is not satisfied, then $n_c$ and $\delta$ are multiplied by a scale function $\lambda>1$, candidates are chosen again, and $\mathcal I(X_c^*)$ is reevaluated.
Once the condition is satisfied, the robot must move to this pose while avoiding collisions subject to the inequality constraint \refeqn{CollisionInequalityConstraint}.

We choose the wavefront planner~\cite{ZelJarByrYut93} because it provides a relatively simple motion planning strategy from $x_t$ to $x_c^*$ that avoids local minima. Once the robot completes this motion, the entire process is repeated. This is summarized in the autonomous exploration pseudocode in Table \ref{tab:Alg_AutomousExploration}.

@@

\begin{table}
\begin{tabular}{ l }
%  Define $n_c$: number of candidate locations\\
%  Define $n_d$: number of evenly-spaced measurement rays per candidate\\
  Given: $t=1$, $X_{1}$, $Z_{1}$, $P(m|X_{1},Z_{1})$ from the inverse sensor model\\
  TrajectoryComplete = false;\\
  while TrajectoryComplete = false\\
  \ \ if $X_{t+1}$ is unknown\\
  \ \ \ \ MotionPlanning = false;\\
  \ \ \ \ while MotionPlanning = false\\
  \ \ \ \ \ \ for $c = 1,2,\ldots,n_c$\\
  \ \ \ \ \ \ \ \ Candidate location: $x_{c}$ from evenly-spaced circle around\\
  \ \ \ \ \ \ \ \ $X_t$ with radius $\delta$;\\
  \ \ \ \ \ \ \ \ for $d=1,2,\ldots,n_d$\\
  \ \ \ \ \ \ \ \ \ \ Obtain reduced map $r_{c,d}$ with $n_{r_{c,d}}$ intersections\\
  \ \ \ \ \ \ \ \ \ \ through grid cells with depths $z_{c,d,1:n_{r,d}}$ from geometry;\\
  \ \ \ \ \ \ \ \ \ \ $\mathcal I_\text{ray}(x_c,z_{c,d})=\text{RayExpInfoGain}(x_c,P(r_{c,d}),z_{c,d,1:n_{r,d}})$;\\
  \ \ \ \ \ \ \ \ end for\\
  \ \ \ \ \ \ \ \ $R_{c}^*=\argmax_{R_c}\left(\sum_{z_{c,i}\in R_c \text{ FOV}}\mathcal I_\text{ray}(x_c,z_{c,i})\right)$;\\%\argmax_{R}{\sum_{d=1}^{n_d}\mathcal I_{\text{ray},c,d}|d\in\text{FOV}(R))}$;\\
  \ \ \ \ \ \ \ \ $\mathcal I(x_c,R_c^*)=\sum_{z_{c,i}\in R_c^* \text{ FOV}}\mathcal I_\text{ray}(x_c,z_{c,i})$;\\%\sum_{d\in \text{FOV}(R_c^*)}\mathcal I_{\text{ray}_{c,d}}$;\\
  \ \ \ \ \ \ end for\\
  \ \ \ \ \ \ $x_c^*=\argmax_{x_c}\mathcal I(x_c,R_c^*)$;\\
  \ \ \ \ \ \ $X_c^*=\braces{x_c^*,R_c^*}$;\\
  \ \ \ \ \ \ if $\mathcal I(X_c^*)<\mathcal I_\text{min}$\\
  \ \ \ \ \ \ \ \ $n_c=\text{round}(\lambda n_c)$;\\
  \ \ \ \ \ \ \ \ $\delta=\lambda \delta$;\\
  \ \ \ \ \ \ else\\
  \ \ \ \ \ \ \ \ Obtain $X_{t+1},X_{t+2},\ldots,X_{c}^*$ using a wavefront\\  \ \ \ \ \ \ \ \ planner and minimum rotation;\\
  \ \ \ \ \ \ \ \ Reset $n_c$ and $\delta$ to initial values;\\
  \ \ \ \ \ \ \ \ MotionPlanning = true;\\  
  \ \ \ \ \ \ end if\\
  \ \ \ \ end while\\
%  $X_c^*=\argmax_{X}$\mathcal I_{\text{ray},c
%  \ \ $\mathcal D\subset\braces{1,2,\ldots,n_d}$ represents scan coverage of candidate rays\\
%  \ \ The $c$-th pose candidate: $X_{c}=\braces{x_{c},R_{c}}$;\\
%   end for\\
%  $X_c^*=\argmin_{X_c}({\Delta H(X_c)}|X_c\in\braces{X_1,X_2,\ldots,X_{n_c}})$;\\
%  Motion planner generates a collision-free path between $X_t$ to $X_c^*$\\
%  Move to $X_{t+1}$, obtain $Z_{t+1}$, and find $P(m|X_{1:t+1},Z_{1:t+1})$;
  \ \ end if\\
  \ \ t = t+1;\\
  \ \ Obtain $P(m|X_{1:t},Z_{1:t})$ from the inverse sensor model;\\
  \ \ if map $m$ is completely explored\\
  \ \ \ \ TrajectoryComplete = true;\\
  \ \ end if\\
  end while

>>>>

\documentclass[letterpaper, 10pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts \overrideIEEEmargins
\usepackage{amsmath,amssymb,url,times,subfigure,graphicx,theorem}
\usepackage{graphicx,subfigure,hyperref}
\usepackage{color,comment}
\usepackage{csquotes}

@@

\title{\LARGE \bf
Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping
%Autonomous Exploration by Predictive Information Gain from Probabilisitic Occupancy Grid Mapping
%Autonomous Exploration by Predictive Occupancy Grid Mapping
%Autonomous Exploration by Predicting Occupancy Grid Maps
}

@@

\newcommand{\EditTL}[1]{{\color{red}\protect #1}}
\newcommand{\EditEK}[1]{{\color{blue}\protect #1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Occupancy grid maps are spatial representations of environments, where the space of interest is decomposed into a number of cells that are considered either occupied or free. This paper focuses on exploring occupancy grid maps by predicting the uncertainty of the map. Based on recent improvements in computing occupancy probability, this paper presents a novel approach for selecting robot poses designed to maximize expected map information gain represented by the change in entropy. This result is simplified with several approximations to develop an algorithm suitable for real-time implementation. The predicted information gain proposed in this paper governs an effective autonomous exploration strategy when applied in conjunction with an existing motion planner to avoid obstacles, which is illustrated by numerical examples.
%The predicted information gain proposed in this paper, in conjunction with an existing motion planner to avoid obstacles, yield an effective autonomous exploration strategy, which is illustrated by numerical examples. 
\end{abstract}

@@

Robotic mapping is the process of generating maps, which represent the environment in close proximity of a robot. The popular occupancy grid mapping representation provides information about the free and occupied space as the robot measures its surroundings~\cite{ThrBurFox05}. Occupancy grid mapping is commonly used while estimating robot location and orientation, known as simultaneous localization and mapping (SLAM). Several SLAM approaches are applied to a variety of problems when mobile robots traverse through an environment to generate a map, but the trajectories are assumed given (e.g.~\cite{ThrBurFox05,DurBai06,CheChe09}). A major problem is that an effective trajectory would be unavailable knowing little or nothing about an environment. 
Autonomous exploration solves this problem, by choosing robotic motion through uncertain space, while building a map that is used for subsequent navigation~\cite{Yam97}.
In this paper, robotic motion is chosen to increase knowledge about the map; a robot chooses a trajectory designed to maximize information gain of the occupancy grid map.

@@

In this paper, we propose an autonomous exploration technique based on expected entropy change that avoids the aforementioned issues. 
%The occupancy grid mapping scheme is based on~\cite{KauLeeAiMos16}, which provides the exact solution of occupancy grid mapping of a single measurement ray. 
We develop a solution for expected entropy gain based on exact occupancy grid mapping~\cite{KauLeeAiMos16}. This solution directly calculates expected entropy from a probabilistic map based on similar assumptions of those applied to occupancy grid mapping.
Though more accurate than several other approaches, the proposed solution requires large computational resources, making real-time implementation difficult in certain scenarios.
Thus, we provide the tools to approximate the exact solution that reduces the computational requirements with realistic assumptions.
The motion of the robot is formulated as an optimization problem, where the expected entropy change is minimized, or equivalently the expected information gain is maximized.
Compared with the recent results (e.g. [12], [13], [16], [17]) that employ Rao-Blackwellized particle filters to deal with localization and autonomous exploration simultaneously with an approximate entropy change, this paper is based on an accurate solution to map information gain, under the assumption that the robot pose is known. In short, this paper presents an accurate and computationally-efficient approach to predict
map information gain for autonomous exploration with a novel structure that avoids common assumptions of the inverse sensor model and approximations in the entropy change.

@@

Consider a reduced map, namely $r_l$, composed of only $n_{r,l}$ grid cells that the $l$-th measurement ray intersects, indexed by increasing distance from the robot. Let the $k$-th cell of $r_l$, namely $\mathbf{r}_{l,k}$, correspond to $\mathbf{m}_i$, i.e., $\mathbf{r}_k=\mathbf{m}_i$ and $\bar{\mathbf{r}}_k=\bar{\mathbf{m}}_i$.
From~\cite{KauLeeAiMos16}, the inverse sensor model of the individual grid cell $\mathbf{m}_i$ is
\begin{align}
\label{eqn:InvSenModWithProbDens}
&P(\mathbf{m}_i|z_{t,l},X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l}
P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1})\nonumber\\
&\quad\times \bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\
&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\nonumber\\
&\quad + \bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,k+},X_t)
\bigg],
\end{align}
where $\mathbf{r}_{l,k+}$ corresponds to all $r_l$ such that cells with index less than $k$ are free, the $k$-th cell is occupied, and cells with greater index are irrelevant. Put differently, the $k$-th cell is the closest occupied cell along the $l$-th ray. The normalizer used in \refeqn{InvSenModWithProbDens} is defined as
\begin{align}
\label{eqn:allEta}
\eta_{t,l}
&=
\bigg[\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}\nonumber\\&\quad\times p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]^{-1}.
\end{align}
This approach to obtain the inverse sensor model is advantageous because of computational efficiency and accuracy, obtaining the exact solution in $\mathcal O(n_{r,l}+1)$ operations for \emph{all} grid cells visible by this measurement ray. In occupancy grid mapping, one may use \refeqn{InvSenModWithProbDens} and \refeqn{allEta} in real-time to avoid common approximations or learned solutions.

@@

We consider $100$ probabilistic maps to obtain Monte Carlo results to evaluate the approximate entropy. In every Monte Carlo trial, each grid cell has an $80\%$ chance of being free and a $20\%$ chance of receiving an a priori probability uniformly distributed between $0$ and $1$. 
%We consider $100$ probabilistic maps to obtain Monte Carlo results to evaluate the approximate entropy. In every Monte Carlo trial, each grid cell has an $80\%$ chance of being free, and the remaining $20\%$ of grid cells are given an a priori probability uniformly distributed between $0$ and $1$. 
Several metrics serve to evaluate $\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]$ with $\text{E}[H_\text{approx}(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]$. The median expected entropy change is $\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]-H(P(m|X_{1:t},Z_{1:t}))=-0.83792$. The error for the $100$ Monte Carlo cases is defined simply as
\begin{align}
e_{H}&=\frac1{100}\sum_{i=1}^{100}\text{abs}\bigg(\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]\nonumber\\&\qquad\quad-\text{E}[H_\text{approx}(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]\bigg).
\end{align}
The Monte Carlo trials are repeated for $\hat n=\braces{1,2,\ldots,10}$ and the results are plotted in Figure \ref{fig:ApproxJust}.
This example shows a typical case when the summation limits generated from \refeqn{ProbOfFirstCell} have only small effects on \refeqn{HRayComplete}, while providing very large improvements in reducing computation.

\begin{figure}
\centerline{
	\subfigure[Entropy Error]
		{\includegraphics[height=0.35\columnwidth]{simpar_approx_err.pdf}
	}	
	\subfigure[Computation Ratio]
		{\includegraphics[height=0.35\columnwidth]{simpar_approx_t.pdf}
	}
}
\caption{The entropy error is decreased at the cost of increasing computation time in this Monte Carlo 1D measurement ray expected entropy case.}
\label{fig:ApproxJust}
\end{figure}

@@

The robot pose at a future time step is selected to maximize \refeqn{ObjFun} over the search space $\Re^2\times\Sph^1$. We reduce the search by discretizing the search space in both position and attitude as follows. First, we choose $n_c$ candidate locations evenly-spaced along a circle of radius $\delta$, centered around the current location $x_t$, where the $c$-th candidate location is denoted $x_c\in\braces{x_1,x_2,\ldots,x_{n_c}}$, illustrated in Figure \ref{fig:OptProcess}. Any location that violates \refeqn{CollisionInequalityConstraint} is excluded to avoid collisions. For each collision-free candidate location, we consider $n_d$ evenly-spaced directions. The rays and attitudes at $x_c$ are denoted $\braces{z_{c,1},z_{c,2},\ldots,z_{c,n_d}}$ and $\braces{R_{c,1},R_{c,2},\ldots,R_{c,n_d}}$, respectively, where the scan with attitude $R_{c,d}$ might cover several ray directions depending on the sensor field of view (FOV). For each candidate location, we choose optimal attitude $R_c^*$ as the summation of the expected entropy changes covered by the scan,
\begin{align}
\label{eqn:FindRc}
&R_c^*=\argmax_{R_{c,d}}\sum_{z_{c,i}\in R_{c,d}\text{ FOV}}\bigg(H(P(m|X_{1:t},Z_{1:t}))\nonumber\\&\qquad\quad\quad\quad\quad-\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,i}))]\bigg).
%\mathcal I_\text{ray}(x_c,z_{c,i})\right).
\end{align}

@@

\begin{figure}
\vspace*{0.08\columnwidth}
\centerline{
	\includegraphics[height=0.35\columnwidth]{ExampleOptimalPose.png}
}
\begin{picture}(0,0)(0,0)
\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\put(4.4,2.1){\color{blue}$X_t$}
\put(5.9,1.9){\color{red}$x_1$}
\put(2.9,2.0){\color{red}$x_5$}
\put(4.4,3.6){\color{red}$x_3$}
\put(4.4,0.6){\color{red}$x_7$}
\put(5.4,3.0){\color{red}$x_2$}
\put(3.3,3.1){\color{red}$x_4$}
\put(3.3,1.0){\color{red}$x_6$}
\put(5.4,1.0){\color{red}$x_8$}
\put(6.8,3.1){\color{red}$z_{2,1}$}
\put(4.5,3.1){\color{red}$z_{2,5}$}
\put(5.6,4.1){\color{red}$z_{2,3}$}
\put(5.6,2.2){\color{red}$z_{2,7}$}
\put(6.5,3.7){\color{red}$z_{2,2}$}
\put(4.9,3.8){\color{red}$z_{2,4}$}
\put(5.0,2.5){\color{red}$z_{2,6}$}
\put(6.5,2.5){\color{red}$z_{2,8}$}
\put(6.1,2.9){$X_c^*$}
\end{picture}
\caption{Initially, a robot (blue circle) views down and left (blue sector). Considering $n_c=8$ poses (red circles) as possible candidate locations to move next, $n_d=8$ sensor directions for each candidate are considered (red lines, only displayed on candidate location $c=2$). Then, the expected entropy of each ray is calculated. The scan (red sector) covering those rays with the largest expected entropy decreases is chosen for each candidate, and the best candidate $X_c^*$ (black circle: location, black sector: scan) is chosen to maximize information gain. Finally, Dijkstra's algorithm provides the collision-free motion between $X_t$ and $X_c^*$, and the process is repeated.
}
\label{fig:OptProcess}
\end{figure}

@@

The objective function of the optimal pose $X_c^*=\braces{x_c^*,R_c^*}$ must satisfy $\mathcal I(X_c^*)\geq\mathcal I_\text{min}$ to avoid motions where little information is expected to be gained. 
If this condition is not satisfied, then $n_c$ and $\delta$ are multiplied by a scale function $\lambda>1$, candidates are chosen again, and $\mathcal I(X_c^*)$ is reevaluated.
Once the condition is satisfied, the robot must move to this pose while avoiding collisions subject to the inequality constraint \refeqn{CollisionInequalityConstraint}. In certain robotic applications, other cost parameters might be included in the optimization, e.g., driving time.

We choose Dijkstra's algorithm~\cite{Dij59} because it provides a relatively simple motion planning strategy from $x_t$ to $x_c^*$ that avoids local minima. Once the robot completes this motion, the entire process is repeated. This is summarized in the autonomous exploration pseudocode in Table \ref{tab:Alg_AutomousExploration}.

@@

\begin{table}
\vspace*{0.02\columnwidth}
\begin{tabular}{ l }
%  Define $n_c$: number of candidate locations\\
%  Define $n_d$: number of evenly-spaced measurement rays per candidate\\
  Given: $t=1$, $X_{1}$, $Z_{1}$, $P(m|X_{1},Z_{1})$ from the inverse sensor model\\
  TrajectoryComplete = false;\\
  while TrajectoryComplete = false\\
  \ \ if $X_{t+1}$ is unknown\\
  \ \ \ \ MotionPlanning = false;\\
  \ \ \ \ while MotionPlanning = false\\
  \ \ \ \ \ \ for $c = 1,2,\ldots,n_c$\\
  \ \ \ \ \ \ \ \ Candidate location: $x_{c}$ from evenly-spaced circle around\\
  \ \ \ \ \ \ \ \ $X_t$ with radius $\delta$;\\
  \ \ \ \ \ \ \ \ for $d=1,2,\ldots,n_d$\\
  \ \ \ \ \ \ \ \ \ \ Obtain reduced map $r_{c,d}$ with $n_{r_{c,d}}$ intersections\\
  \ \ \ \ \ \ \ \ \ \ through grid cells with depths $z_{c,d,1:n_{r,d}}$ from geometry;\\
  \ \ \ \ \ \ \ \ \ \ $\mathcal I_\text{ray}(x_c,z_{c,d})=\text{RayExpInfoGain}(x_c,P(r_{c,d}),z_{c,d,1:n_{r,d}})$;\\
  \ \ \ \ \ \ \ \ end for\\
  \ \ \ \ \ \ \ \ $R_{c}^*=\argmax_{R_c}\left(\sum_{z_{c,i}\in R_c \text{ FOV}}\mathcal I_\text{ray}(x_c,z_{c,i})\right)$;\\%\argmax_{R}{\sum_{d=1}^{n_d}\mathcal I_{\text{ray},c,d}|d\in\text{FOV}(R))}$;\\
  \ \ \ \ \ \ \ \ $\mathcal I(x_c,R_c^*)=\sum_{z_{c,i}\in R_c^* \text{ FOV}}\mathcal I_\text{ray}(x_c,z_{c,i})$;\\%\sum_{d\in \text{FOV}(R_c^*)}\mathcal I_{\text{ray}_{c,d}}$;\\
  \ \ \ \ \ \ end for\\
  \ \ \ \ \ \ $x_c^*=\argmax_{x_c}\mathcal I(x_c,R_c^*)$;\\
  \ \ \ \ \ \ $X_c^*=\braces{x_c^*,R_c^*}$;\\
  \ \ \ \ \ \ if $\mathcal I(X_c^*)<\mathcal I_\text{min}$\\
  \ \ \ \ \ \ \ \ $n_c=\text{round}(\lambda n_c)$;\\
  \ \ \ \ \ \ \ \ $\delta=\lambda \delta$;\\
  \ \ \ \ \ \ else\\
  \ \ \ \ \ \ \ \ Obtain $X_{t+1},X_{t+2},\ldots,X_{c}^*$ using Dijkstra's algorithm\\  \ \ \ \ \ \ \ \ planner and minimum rotation;\\
  \ \ \ \ \ \ \ \ Reset $n_c$ and $\delta$ to initial values;\\
  \ \ \ \ \ \ \ \ MotionPlanning = true;\\  
  \ \ \ \ \ \ end if\\
  \ \ \ \ end while\\
%  $X_c^*=\argmax_{X}$\mathcal I_{\text{ray},c
%  \ \ $\mathcal D\subset\braces{1,2,\ldots,n_d}$ represents scan coverage of candidate rays\\
%  \ \ The $c$-th pose candidate: $X_{c}=\braces{x_{c},R_{c}}$;\\
%   end for\\
%  $X_c^*=\argmin_{X_c}({\Delta H(X_c)}|X_c\in\braces{X_1,X_2,\ldots,X_{n_c}})$;\\
%  Motion planner generates a collision-free path between $X_t$ to $X_c^*$\\
%  Move to $X_{t+1}$, obtain $Z_{t+1}$, and find $P(m|X_{1:t+1},Z_{1:t+1})$;
  \ \ end if\\
  \ \ t = t+1;\\
  \ \ Obtain $P(m|X_{1:t},Z_{1:t})$ from the inverse sensor model;\\
  \ \ if map $m$ is completely explored\\
  \ \ \ \ TrajectoryComplete = true;\\
  \ \ end if\\
  end while
